---
title: "FRB Technical Assessment"
author: 'Chia Chye Yee'
subtitle: "Reproduction of Table 37"
date: "`r Sys.Date()`"
output: 
## Deprecate pdf output as formatting is just a tiny bit off. 
  # pdf_document: 
  #   toc: no
  #   toc_depth: 4
  html_document:
        toc: yes
        toc_depth: 4
        toc_float:
          toc_collapsed: true
---
```{r setup, echo=FALSE, message=FALSE}
## Checking for required packages and installing them if they are not installed.
required_packages = c('rmarkdown', 'data.table', 'dplyr', 'stringi', 'stringr', 
                      'kableExtra', 'tidyr')
install_required_packages = required_packages[!(required_packages %in% 
                                                  installed.packages()[,'Package'])]
if(length(install_required_packages)){
  cat(paste0('Installing: ', install_required_packages,' \n'))
  install.packages(install_required_packages, 
                   repos = "http://cran.us.r-project.org")
}
## Loading required packages.
options(warn = -1)
invisible(lapply(required_packages, require, character.only = TRUE))
options(warn = 0)
```

## 1 Introduction

The purpose of this document is to reproduce results from table 37 of the [2023 Supervisory Stress Test Methodology Disclosure](https://www.federalreserve.gov/publications/files/2023-june-supervisory-stress-test-methodology.pdf). The constituent computation is presented in Section 2 and the final result is presented in Section 3. Before presenting the constituent computation, the following are the additional data processing presented here to aid readers.

```{r additional_computation, message=FALSE}
## Loading data from csv files.
cards_low_risk = 
  read.csv('https://www.federalreserve.gov/supervisionreg/files/cards-low-risk-2023.csv')
cards_typical_risk = 
  read.csv('https://www.federalreserve.gov/supervisionreg/files/cards-typical-risk-2023.csv')
cards_high_risk = 
  read.csv('https://www.federalreserve.gov/supervisionreg/files/cards-high-risk-2023.csv')

## Additional processing
cards_low_risk = data.table::as.data.table(cards_low_risk) %>% mutate(portfolio = 'Lower-risk')
cards_typical_risk = data.table::as.data.table(cards_typical_risk) %>% mutate(portfolio = 'Typical')
cards_high_risk = data.table::as.data.table(cards_high_risk) %>% mutate(portfolio = 'Higher-risk')

## Normalizing balance to simplify computation
cards_low_risk = cards_low_risk %>% 
  mutate(cycleendingbalance_prop = cycleendingbalance/sum(cycleendingbalance))
cards_typical_risk = cards_typical_risk %>% 
  mutate(cycleendingbalance_prop = cycleendingbalance/sum(cycleendingbalance))
cards_high_risk = cards_high_risk %>% 
  mutate(cycleendingbalance_prop = cycleendingbalance/sum(cycleendingbalance))

## Concatenating the tables to simplify code
cards_overall = data.table::funion(cards_low_risk, cards_typical_risk)
cards_overall = data.table::funion(cards_overall, cards_high_risk)

## Additional data processing
cards_overall = cards_overall %>% 
  mutate(current_credit_limit = case_when(currentcreditlimit <= 1500 ~ '$1,500 and less',
                                       currentcreditlimit > 1500 & 
                                         currentcreditlimit <= 7500 ~ '$1,501–$7,500',
                                       currentcreditlimit > 7500 ~ 'Over $7,500'),
         credit_card_type = case_when(creditcardtype == 1 ~ 'General purpose',
                                      creditcardtype == 2 ~ 'Private label'),
         days_past_due = case_when(dayspastdue <= 30 ~ 'Current',
                                   dayspastdue > 30 ~ '30+ Days past due'),
         product_type = case_when(producttype == 1 ~ 'Co-brand',
                                  producttype == 2 ~ 'Other'),
         month_end_account_status = case_when(monthendclosedrevokedflag == 0 ~ 'Open and active',
                                      monthendclosedrevokedflag == 1 ~ 'Other'),
         month_end_close_status = case_when(monthendclosedrevokedflag == 0 ~ 'Not closed',
                                      monthendclosedrevokedflag == 1 ~ 'Closed'),
         account_origination_year = case_when(accountoriginationyear <= 2017 ~ '2017 and prior',
                                              .default = as.character(accountoriginationyear)),
         cycle_ending_balance  = case_when(cycleendingbalance < 1000 ~ 'Under $1,000',
                                               cycleendingbalance >= 1000 &
                                                 cycleendingbalance <= 1999 ~ '$1,000–$1,999',
                                               cycleendingbalance >= 2000 &
                                                 cycleendingbalance <= 2999 ~ '$2,000–$2,999',
                                               cycleendingbalance >= 3000 &
                                                 cycleendingbalance <= 4999 ~ '$3,000–$4,999',
                                               cycleendingbalance >= 5000 &
                                                 cycleendingbalance <= 9999 ~ '$5,000–$9,999',
                                               cycleendingbalance >= 10000 ~ '$10,000 and over'),
         income_at_origination = case_when(borrowerincome <= 50000 ~ '$50,000 and less',
                                           borrowerincome > 50000 &
                                             borrowerincome <= 100000 ~ '$50,001–$100,000',
                                           borrowerincome > 100000 ~ 'Over $100,000'
                                           ),
         original_credit_limit = case_when(originalcreditlimit <= 1500 ~ '$1,500 and less',
                                           originalcreditlimit > 1500 & 
                                             originalcreditlimit <= 7500 ~ '$1,501–$7,500',
                                           originalcreditlimit > 7500 ~ 'Over $7,500'),
         interest_rate_at_cycle_end = case_when(cycleendingretailapr < 12 ~ 'Under 12%',
                                                cycleendingretailapr >= 12 &
                                                  cycleendingretailapr <= 14.99 ~ '12%–14.99%',
                                                cycleendingretailapr >= 15 &
                                                  cycleendingretailapr <= 19.99 ~ '15%–19.99%',
                                                cycleendingretailapr >= 20 &
                                                  cycleendingretailapr <= 23.99 ~ '20%–23.99%',
                                                cycleendingretailapr >= 24 ~ '24% and over')
         )

## Defining commonly used functions
subsegment_percent = function(subsegment){
  return(
    cards_overall %>%
  group_by(.dots = subsegment, portfolio) %>% 
  summarize( percentage = round(sum(cycleendingbalance_prop)*100, 2))
  )
}
table_format = function(tab){
  return(
    tab %>%
  kable(align = 'c') %>%
  kable_styling(full_width = F)
  )
}
table_pivot = function(tab, varname){
  tab_ret = tab %>% 
  rename(Variables = paste0(varname)) %>% 
  pivot_wider(id_cols = 'Variables', names_from = 'portfolio', values_from = percentage) %>% 
  relocate(any_of(c('Variables', 'Lower-risk', 'Typical', 'Higher-risk')))
  return(tab_ret)
}
```

## 2 Computation

```{r table37, message=FALSE, warning=FALSE}
credit_card_type =  subsegment_percent('credit_card_type')
table_format(credit_card_type)

current_credit_limit = subsegment_percent('current_credit_limit')
table_format(current_credit_limit)

days_past_due = subsegment_percent('days_past_due')
days_past_due = data.table::as.data.table(days_past_due) %>% 
  add_row(days_past_due = "30+ Days past due",
          portfolio = 'Lower-risk',
          percentage = round(0*100, 2)) %>% ## Adding a row for a 0 percent sub-group
  arrange(days_past_due, portfolio)
table_format(days_past_due)

product_type = subsegment_percent('product_type')
table_format(product_type)

month_end_account_status= subsegment_percent('month_end_account_status')
month_end_account_status= data.table::as.data.table(month_end_account_status) %>% 
  add_row(month_end_account_status= "Other",
          portfolio = 'Lower-risk',
          percentage = round(0*100, 2)) %>% 
  add_row(month_end_account_status= "Other",
          portfolio = 'Typical',
          percentage = round(0*100, 2)) %>%  ## Adding rows for subsegments with zeroes
  arrange(month_end_account_status, portfolio)
table_format(month_end_account_status)

account_origination_year = subsegment_percent('account_origination_year')
table_format(account_origination_year)

month_end_close_status = subsegment_percent('month_end_close_status')
month_end_close_status = data.table::as.data.table(month_end_close_status) %>% 
  add_row(month_end_close_status = "Closed",
          portfolio = 'Lower-risk',
          percentage = round(0*100, 2)) %>% 
  add_row(month_end_close_status = "Closed",
          portfolio = 'Typical',
          percentage = round(0*100, 2)) %>%  ## Adding rows for subsegments with zeroes
  arrange(month_end_close_status, portfolio)
table_format(month_end_close_status)

cycle_ending_balance  = subsegment_percent('cycle_ending_balance' )
table_format(cycle_ending_balance)

income_at_origination = subsegment_percent('income_at_origination')
table_format(income_at_origination)

original_credit_limit = subsegment_percent('original_credit_limit')
table_format(original_credit_limit)

interest_rate_at_cycle_end = subsegment_percent('interest_rate_at_cycle_end')
table_format(interest_rate_at_cycle_end)
```

## 3 Final Results

The following is the final result. For reference, the code for this is saved in the following [github repository](https://github.com/chye17/frb_technical).

```{r overall}
## Listing the number of subsegments of interest
subseg_list = c('credit_card_type', 'current_credit_limit', 'days_past_due', 
                'product_type', 'month_end_account_status', 'account_origination_year',
                'month_end_close_status', 'cycle_ending_balance', 'income_at_origination',
                'original_credit_limit', 'interest_rate_at_cycle_end')
## Creating main table to prep for concatenation of results
data_concat = data.table::data.table(`Variables` = as.character(NA), `Lower-risk` = as.numeric(NA), `Typical` = as.numeric(NA), `Higher-risk` = as.numeric(NA))
## Cycling through list of subsegments of interest and concatenating it to main table
for(i in subseg_list){
  data_temp = data.table::data.table(`Variables` = i, 
                                     `Lower-risk` = as.numeric(NA), 
                                     `Typical` = as.numeric(NA), 
                                     `Higher-risk` = as.numeric(NA))
  data_actual = data.table::as.data.table(table_pivot(tab = mget(paste0(i))[[1]], 
                                                                       varname = paste0(i)))
  
  data_temp = data.table::funion(data_temp, data_actual)
  data_concat = data.table::funion(data_concat, data_temp)
}
data_concat = data_concat %>% filter(!is.na(Variables))
data_concat[is.na(data_concat)] <- " "

table_format(data_concat)

```
